Implications of uniformly distributed, empirically informed priors for phylogeographical model selection: A reply to Hickerson et al.

### 2014-07-18 manuscripts/reply/reply-main.tex
More work on intro of reply ms.

Recently, \citet{Oaks2012} used this model-choice framework to 
study 22 pairs of vertebrate lineages which are distributed across
the Philippines; they also studied the behavior of the \msb approach
using computer simulations.
They found the method was very sensitive to prior assumptions and suggested
this was due to the fact that the marginal likelihoods of models are sensitive
to the use of uniform priors on divergence times.
In response, \citet{Hickerson2013} suggested the lack of robustness in \msb
analyses was caused by sampling error due to the inefficiency of the method's
rejection algorithm.
They proposed a model-averaging approach that uses narrow, empirically
informed uniform priors.

@@

\change{
Here, we discuss theoretical considerations for using empirically informed
priors for Bayesian model choice.
}
We then evaluate the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} as a potential solution to the biases of \msb revealed by
\citet{Oaks2012}.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different units of time, which makes the results
presented in their response difficult to interpret (see Supporting Information
for details).
We avoid this error, but still find their approach to be biased toward
clustered divergence models.
Furthermore, the approach provides another means by which the method can
``escape'' models with large parameter space, which manifests in the preference
of models that exclude from consideration the true values of the model's
parameters.
\change{
Our results, show that it is difficult to choose a uniformly distributed prior
on divergence times that is broad enough to confidently contain the true values
of parameters while being narrow enough to avoid spurious support of models
with less parameter space.
}
We also explore the predictions of the alternative causes of this problem
proposed by \citet{Oaks2012} and \citet{Hickerson2013}.
We find the prior sensitivity of the marginal likelihoods is a likely
culprit,
and show that sampling error is not a major contributer to the biases found
by \citet{Oaks2012}.
Fortunately, \citet{Oaks2014dpp} has introduced a new method that uses more
flexible probability distributions to accommodate prior uncertainty in
divergence times without inhibiting the marginal likelihoods of models with
more divergence-time parameters, which increases the method's robustness and
power to detect temporal variation in divergences \citep{Oaks2014dpp}.

>>>>

Recently, \citet{Oaks2012} used this model-choice framework to 
study 22 pairs of vertebrate lineages which are distributed across
the Philippines; they also studied the behavior of the \msb approach
using computer simulations.
They found the method was very sensitive to prior assumptions and suggested
this was due to the fact that the marginal likelihoods of divergence models are
sensitive to the use of uniform priors on divergence times.
\citet{Oaks2012} suggested that alternative probability distributions (e.g.,
gamma) could better represent prior uncertainty about divergence times while
mitigating the disparity of marginal likelihoods across divergence models.
In response, \citet{Hickerson2013} suggested the lack of robustness in \msb
analyses was caused by sampling error due to the inefficiency of the method's
rejection algorithm.
As a potential solution, they proposed a model-averaging approach that uses
narrow, empirically informed uniform priors.

@@

\change{
Here, we discuss theoretical considerations for using empirically informed
priors for Bayesian model choice.
}
We then evaluate the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} as a potential solution to the biases of \msb revealed by
\citet{Oaks2012}.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different units of time, which makes the results
presented in their response difficult to interpret (see Supporting Information
for details).
We avoid this error, but still find their approach to be biased toward
clustered divergence models.
Furthermore, the approach provides another means by which the method can
``escape'' models with large parameter space, which manifests in the preference
of models that exclude from consideration the true values of the model's
parameters.
\change{
Our results, show that it is difficult to choose a uniformly distributed prior
on divergence times that is broad enough to confidently contain the true values
of parameters while being narrow enough to avoid spurious support of models
with less parameter space.
}
We also explore the predictions of the alternative causes of this problem
proposed by \citet{Oaks2012} and \citet{Hickerson2013}.
Our finings suggest the primary cause is the disparity in marginal likelihoods
across possible divergence models imposed by the uniform priors on divergence
times.
Furthermore, we show that sampling error is not a major contributer to the
biases found by \citet{Oaks2012}.
Fortunately, \citet{Oaks2014dpp} has introduced a method that uses more
flexible probability distributions to accommodate prior uncertainty in
divergence times without inhibiting the marginal likelihoods of models with
more divergence-time parameters, which increases the method's robustness and
power to detect temporal variation in divergences \citep{Oaks2014dpp}.
